Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Add another paper on data quality assessment
Add paper on automatic bug report assignment

  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

@@

>>>>

  \item \textbf{What was the method?}
    They created the TDQM methodology which is based on accumulated research 
    and extended 
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

@@

\textbf{Automatic Bug Report Assignment}\cite{anvik2006automating}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The author’s main goal was to determine a way through which bug triaging can be made 
    easier using automatization approaches. 
  \item \textbf{What was the method?}
    The research’s output was an algorithm that can automatically assign bugs to developers based on various types of information fed. The author looked exclusively at ML approaches, examining 8 main types of information (textual description of bug, bug component, OS, hardware, software version, developer who owns the code, current workload of developers, list of devs actively contributing). Moreover, the author considers launching a Firefox extension to test the app even further through human evaluation as well. 
  \item \textbf{What did they learn?}
  The research brings 3 main contributions: methodology for creating semi-automated bug triaging algorithms, a characterization of performance of different approaches, as well as an actual implementation for such a semi-automated big triaget. The author discovered that with further improvements and tweaking, we can reach an even further bug triager.   
  \item \textbf{Relevance to our work}:
  Another project that we can use to learn about bug triaging; also we can contact maybe the author and receive either an executable or the source code for the application. 
\end{itemize}
